### 2020-06-06 5_evaluation.tex
Fiddle with wording.

There are two points of interest on each ``limit 50\%'' curve: the point
where it intersects ``actual'' and the point where it intersects an
ideal scaling curve, computed by taking the initial time to solution
and assuming linear scaling. These points are marked for Charm++ in
Figure~\ref{fig:strong-scaling} with a black square and black circle,
respectively.
Notably, the ideal-limit intersection (black circle) requires only a
run of the application on one node, combined with METG(50\%)
measurements at each node count, to estimate the strong scalability of
the code:
%% Notably, computing the ideal scaling line requires only
%% the running time on a single node, so the intersection between ideal
%% and ``limit'' can be found with only the single-node time to
%% solution, along with measurements of METG(50\%) at each node
%% count. Using this data it is possible to predict the
%% strong scalability of the code:
i.e., the smallest time to solution,
and the number of nodes at which that time is achieved, while
maintaining at least 50\% efficiency. In
Figure~\ref{fig:strong-scaling} this can be seen as the distance
between the black square and circle; these are separated by a factor of
$1.22\times$ in node count, and $1.27\times$ in time to solution.

>>>>

There are two points of interest on each ``limit 50\%'' curve: the point
where it intersects ``actual'' and the point where it intersects an
ideal scaling curve, computed by taking the initial time to solution
and assuming linear scaling. These points are marked for Charm++ in
Figure~\ref{fig:strong-scaling} with a black square and black circle,
respectively.
Notably, the ideal-limit intersection (black circle) requires only a
run of the application on one node, combined with METG(50\%)
measurements, to estimate the strong scalability of
the code:
%% Notably, computing the ideal scaling line requires only
%% the running time on a single node, so the intersection between ideal
%% and ``limit'' can be found with only the single-node time to
%% solution, along with measurements of METG(50\%) at each node
%% count. Using this data it is possible to predict the
%% strong scalability of the code:
i.e., the smallest time to solution,
and the number of nodes at which that time is achieved, while
maintaining at least 50\% efficiency. In
Figure~\ref{fig:strong-scaling} this can be seen as the distance
between the black square and circle; these are separated by a factor of
$1.22\times$ in node count, and $1.27\times$ in time to solution.
